%!TEX root = thesis.tex

\prefacesection{Abstract}

Teaching machines to recognize and even understand satellite images is one of the most elusive and persistent challenges in artiﬁcial intelligence. This thesis tackles satellite image recognition: using the data and models needed to train models to identify small boats and measure their length. On the one hand, detecting small boats in satellite images is a major test of artiﬁcial intelligence algorithms. But, on the other hand, if we can build efﬁcient object detection models, it will become a key technology for building carbon inventories in the shipping industry.

This thesis focuses on convolutional neural network models: a class of neural network models built on top of convolutional operations. These end-to-end neural models are more effective in learning media content (e.g., texts, images, and videos) and substantially improve performance on all object detection benchmarks than traditional feature-based models.

This thesis consists of two parts. In the ﬁrst part, our goal is to cover every aspect of object detection algorithm and show our efforts in building effective object detection models and, more importantly, to understand what convolutional neural network models have actually learned. In the second part of this thesis, I show my detection results and analyze the various possibilities behind the results.

In particular, I discuss two new research directions at the end of this thesis: 1) whether a CAD model can replace the data from the training model, and 2) whether the algorithm has the ability (memory and understanding) to identify the same ship that appears at different times. I believe that they hold great promise for future satellite image analysis.